---
title: "ANALYSIS"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("LMest")
library(LMest)
library(tidyverse)
```

Loading the data
````{r}
#qual_data <- read_csv("qual_socioeco_df.csv")
qual_data <- read_csv("/work/Bachelor/Qualitative/qual_socioeco_df.csv")

#prepare data
dt <- lmestData(qual_data, id = "ID", time = "time")
````


# Baseline model
Used to figure out the best number of k:
```{r}
m_1 <- lmestCont(responsesFormula = resp_syn + resp_morph ~ NULL,
                  index = c("ID", "time"), 
                  k = 1:6, 
                  data = dt$data, 
                  modBasic = 0, 
                  output = TRUE, 
                  tol = 10^-5, 
                  out_se = TRUE, seed = 100   
                )

m_1$k

plot(m_1, what = "modSel")
```


**Initial probabilities for baseline model**
```{r}
m_1$piv
```

**Transition probabilities for baseline model**
Time heterogeneous probabilities are here found: 
```{r}
m_1$Pi
```

**Marginal distribution for baseline model**
```{r}
# Determine the marginal distribution
TT<-m_1$TT
Pmarg <- as.matrix(m_1$piv)
for(t in 2:TT) Pmarg= cbind(Pmarg,t(m_1$Pi[,,t])%*%Pmarg[,t-1])
Pmarg
```
#### **Conditional Response Parameter**
Tells the mean response in each state, used for labeling the states.
```{r}
m_1$Mu
round(m_1$seMu, 3)
```



## WITH COVARIATES => BEST PERFORMING MODEL 
with a set number of k
```{r}
m_10.1 <- lmestCont(responsesFormula = resp_syn + resp_morph ~ NULL, 
                  latentFormula = ~ TimerIDagtilbud + CivilStatus | TimerIDagtilbud,
                  index = c("ID", "time"), 
                  k = 2, 
                  data = dt$data, 
                  modBasic = 0, 
                  output = TRUE, 
                  tol = 10^-5, 
                  out_se = TRUE, seed = 1   
                )
```


#### **Covariates effect on initial prob**
The argument *Be*, returned by the function, contains the estimated regression parameters affecting the distribution of the **initial probabilities**
```{r}
### these are in logit and should be made into log odds 
m_10.1$Be
inv.logit(m_10.1$Be)
```

#### **SE and significance for initial probabilities**
```{r}
be_odds <- inv.logit(m_10.1$Be)
be_se_odds <- inv.logit(m_10.1$seBe)
p_be <- 2 * pnorm(q=m_10.1$Be/m_10.1$seBe, lower.tail = FALSE)


TabBe <-cbind(be_odds, be_se_odds, m_10.1$Be/m_10.1$seBe, p_be)
colnames(TabBe) <- c("estBe",  "s.e.Be","z-score", "p-value") 
round(TabBe, 3) 
```

#### **Covariates effect on transition prob**
Output *Ga* contains the estimated parameters affecting the distribution of the **transition probabilities**. They measure the influence of each covariate on the transition between states.
```{r}
m_10.1$Ga
inv.logit(m_10.1$Ga)
```


#### **SE and significance for transition probabilities**
```{r}
ga_odds <- inv.logit(m_10.1$Ga)
ga_se_odds <- inv.logit(m_10.1$seGa)
ga_z_score <- m_10.1$Ga/m_10.1$seGa
p <- 2*pnorm(q=m_10.1$Ga/m_10.1$seGa, lower.tail = FALSE)


TabGa1 <- cbind(ga_odds, ga_se_odds, ga_z_score, p) 
colnames(TabGa1) <- c("estGa(1-2)","estGa(2-1)", "s.e.Ga(1-2)","s.e.Ga(2-1)", "z-score(1-2)","z-score(2-1)", "p-value(1-2)", "p-value(2-1)")

round(TabGa1,3) 
```

#### **Marginal Distribution** 
```{r}
## Determine the marginal distribution
n <- m_10.1$n; n
TT <- m_10.1$TT; TT
k <- m_10.1$k; k

PMarg1 <- array(0,c(n,k,TT)); dim(PMarg1)
PMarg1[,,1] <- as.matrix(m_10.1$Piv)
for(i in 1:n) for(t in 2:TT) PMarg1[i,,t]= t(m_10.1$PI[,,i,t])%*%PMarg1[i,,t-1]
Pmarg1 <-apply(PMarg1,c(2,3),mean)
Pmarg1


````


##### Covariate model

```{r}
dt <- lmestData(qual_data, id = "ID", time = "time")

qual_all_cov_socio <- lmestCont(responsesFormula = resp_syn + resp_morph ~ NULL, 
                  latentFormula = ~ gender + Beskaeftigelse + TimerIDagtilbud+ Uddannelse + IUddannelse + Arbejdstimer+ Modersmaal + Pasningsform , 
                  index = c("ID", "time"), 
                  k = 2, 
                  data = dt$data, 
                  modBasic = 0, 
                  output = TRUE, 
                  tol = 10^-5, 
                  out_se = TRUE,
                  seed = 123
                )
```

#### **Covariates effect on initial prob**
The argument *Be*, returned by the function, contains the estimated regression parameters affecting the distribution of the **initial probabilities**
```{r}
### these are in logit and should be made into log odds 
qual_all_cov_socio$Be

```

#### **SE and significance for initial probabilities**
```{r}
be_odds <- qual_all_cov_socio$Be
be_se_odds <- qual_all_cov_socio$seBe
p_be <- 2*pnorm(q=qual_all_cov_socio$Be/qual_all_cov_socio$seBe, lower.tail = FALSE)

TabBe <-cbind(be_odds, be_se_odds, qual_all_cov_socio$Be/qual_all_cov_socio$seBe, p_be)
colnames(TabBe) <- c("estBe",  "s.e.Be","t-test", "p-value") 
round(TabBe,3) 
```


#### **Covariates effect on transition probabilities**
model with ALL covariates
```{r}
ga_odds <- qual_all_cov_socio$Ga
ga_se_odds <- qual_all_cov_socio$seGa
p <- 2*pnorm(q=qual_all_cov_socio$Ga/qual_all_cov_socio$seGa, lower.tail = FALSE)

TabGa1 <- cbind(ga_odds, ga_se_odds, qual_all_cov_socio$Ga/qual_all_cov_socio$seGa, p) 
colnames(TabGa1) <- c("estGa(1-2)","estGa(2-1)", "s.e.Ga(1)","s.e.Ga(2)", "z-score(1)","z-score(2)", "p-value(1)", "p-value(2)")

round(TabGa1,3) 

```





