---
title: "QUAL_HOMELIT_ANALYSIS"
output: html_document
date: '2022-12-01'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("LMest")
library(LMest)
library(tidyverse)
```

Loading the data
````{r}
qual_data <- read_csv("/work/Bachelor/Qualitative/qual_homelit_df.csv")
# filtering out non socio economic variables:
length(unique(qual_data$ID))
head(qual_data)
````

# Baseline model
Used to figure out the best number of k:
```{r}
#prepare data
dt <- lmestData(qual_data, id = "ID", time = "time")


#model
m_1 <- lmestCont(responsesFormula =resp_syn + resp_morph ~ NULL, 
                latentFormula = NULL,
                index = c("ID", "time"), k = 1:6, data = dt$data, 
                modBasic = 0, 
                output = TRUE, 
                tol = 10^-5, 
                out_se = TRUE,
                seed = 1)

m_1$k # best amount of k
round(m_1$Bic,3) #BIC at all states
round(m_1$Aic,3) #AIC at all states
round(m_1$np, 3) # number of free parameters
round(m_1$Lk,3) # maximum log likelihood
plot(m_1, what= "modSel")
```

**Initial probabilities**
```{r}
m_1$piv
```

**Transition probabilities**
Time heterogeneous probabilities are here found: 
```{r}
m_1$Pi
```

#### **Marginal Distribution** 
```{r}
# Determine the marginal distribution
TT<-m_1$TT
Pmarg1 <- as.matrix(m_1$piv)
for(t in 2:TT) Pmarg1= cbind(Pmarg1,t(m_1$Pi[,,t])%*%Pmarg1[,t-1])
Pmarg1
```

#### **Conditional Response Parameter**
Tells the mean response in each state, used for labeling the states.
```{r}
m_1$Mu
```




##### Covariate model
Covariate model with all covariates

```{r}
dt <- lmestData(qual_data, id = "ID", time = "time")

## model with all covariates
qual_all_cov_homelit <- lmestCont(responsesFormula = resp_syn + resp_morph ~ NULL, 
                  latentFormula = ~ gender + RimRemserUgen + SangUgen + AntalBoerneboeger + AntalVoksenboeger + InitiativTilLaesning + HoejtlaesningUgen, 
                  index = c("ID", "time"), 
                  k = 2, 
                  data = dt$data, 
                  modBasic = 0, 
                  output = TRUE, 
                  tol = 10^-5, 
                  out_se = TRUE, 
                  seed = 123
                )

```

#### **Covariates effect on initial prob**
The argument *Be*, returned by the function, contains the estimated regression parameters affecting the distribution of the **initial probabilities**
```{r}
### these are in logit and should be made into log odds 
qual_all_cov_homelit$Be
```

#### **SE and significance for initial probabilities**
```{r}
be_odds <- qual_all_cov_homelit$Be
be_se_odds <- qual_all_cov_homelit$seBe
p_be <- 2*pnorm(q=qual_all_cov_homelit$Be/qual_all_cov_homelit$seBe, lower.tail = FALSE)

TabBe <-cbind(be_odds, be_se_odds, qual_all_cov_homelit$Be/qual_all_cov_homelit$seBe, p_be)
colnames(TabBe) <- c("estBe",  "s.e.Be","t-test", "p-value") 
round(TabBe,3) 
```




#### **Covariates effect on transition probabilities**
model with ALL covariates
```{r}
ga_odds <- qual_all_cov_homelit$Ga
ga_se_odds <- qual_all_cov_homelit$seGa
p <- 2*pnorm(q=qual_all_cov_homelit$Ga/qual_all_cov_homelit$seGa, lower.tail = FALSE)

TabGa1 <- cbind(ga_odds, ga_se_odds, qual_all_cov_homelit$Ga/qual_all_cov_homelit$seGa, p) 
colnames(TabGa1) <- c("estGa(1-2)","estGa(2-1)", "s.e.Ga(1)","s.e.Ga(2)", "z-score(1)","z-score(2)", "p-value(1)", "p-value(2)")

round(TabGa1,3) 

```

