---
title: "QUANT_SOCIO_ANALYSIS"
output: html_document
date: '2022-12-06'
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("LMest")
pacman::p_load(LMest, boot, tidyverse)
```

### Loading the data
````{r}
#setwd("~/Library/Mobile Documents/com~apple~CloudDocs/Desktop/Bachelor 2022/analysis")
#quant_data <- read_csv("quant_socioeco_df.csv")
quant_data <- read_csv("/work/Bachelor/Quantitative/quant_socioeco_df.csv")
# filtering out non socio economic variables:
head(quant_data)
length(unique(quant_data$ID))
````


# Baseline Model
Used to figure out the best number of k:
```{r}
#prepare data
dt <- lmestData(quant_data, id = "ID", time = "time")

#model
m_1 <- lmestCont(responsesFormula = resp_ord ~ NULL, 
                latentFormula = NULL,
                index = c("ID", "time"), k = 1:6, data = dt$data, 
                modBasic = 0, 
                output = TRUE, 
                tol = 10^-5, 
                out_se = TRUE)

```

**Initial probabilities**
```{r}
round(m_1$piv, 3)
```

**Transition probabilities**
```{r}
round(m_1$Pi, 3)
```

#### **Marginal Distribution** 
```{r}
# Determine the marginal distribution
TT<-m_1$TT
Pmarg1 <- as.matrix(m_1$piv)
for(t in 2:TT) Pmarg1= cbind(Pmarg1,t(m_1$Pi[,,t])%*%Pmarg1[,t-1])
round(Pmarg1, 3)
```

#### **Conditional Response Parameter**
Tells the mean response in each state, used for labeling the states.
```{r}
round(m_1$Mu, 3)
round(m_1$seMu, 3)
```




# Covariate Model

```{r}
dt <- lmestData(quant_data, id = "ID", time = "time")

## model with all covariates
quant_all_cov_socio <- lmestCont(responsesFormula = resp_ord ~ NULL, 
                  latentFormula = ~ gender + Beskaeftigelse + TimerIDagtilbud+ Uddannelse + IUddannelse + Arbejdstimer+ Modersmaal + Pasningsform, 
                  index = c("ID", "time"), 
                  k = 3, 
                  data = dt$data, 
                  modBasic = 0, 
                  output = TRUE, 
                  tol = 10^-5, 
                  out_se = TRUE, 
                  seed= 123
                )


```

#### **Covariates effect on initial prob**
The argument *Be*, returned by the function, contains the estimated regression parameters affecting the distribution of the **initial probabilities**
```{r}
### these are in logit and should be made into log odds 
quant_all_cov_socio$Be
```

#### **SE and significance for initial probabilities**
```{r}
be_odds <- quant_all_cov_socio$Be
be_se_odds <- quant_all_cov_socio$seBe
p_be <- 2 * pnorm(q=quant_all_cov_socio$Be/quant_all_cov_socio$seBe, lower.tail = FALSE)

TabBe <-cbind(be_odds, be_se_odds, quant_all_cov_socio$Be/quant_all_cov_socio$seBe, p_be)
colnames(TabBe) <- c("estBe(2)", "estBe(3)", "s.e.Be(2)","s.e.Be(3)","z-score (2)", "z-score (3)", "p-value(2)", "p-value1(3)") 
round(TabBe, 3) 
```


#### **Covariates effect on transition probabilities**
model with ALL covariates
```{r}
ga_odds <- quant_all_cov_socio$Ga
ga_se_odds <- quant_all_cov_socio$seGa
ga_z_score <-  quant_all_cov_socio$Ga/quant_all_cov_socio$seGa
p <- 2*pnorm(q=quant_all_cov_socio$Ga/quant_all_cov_socio$seGa, lower.tail = FALSE)


TabGa1 <- cbind(ga_odds[,1,1],ga_odds[,2,1] ,ga_odds[,1,2],ga_odds[,2,2], ga_odds[,1,3],ga_odds[,2,3])
colnames(TabGa1) <- c("estGa(1-2)","estGa(1-3)", "estGa(2-1)","estGa(2-3)", "estGa(3-1)", "estGa(3-2)")


TabGa2 <- cbind(ga_se_odds[,1,1],ga_se_odds[,2,1] ,ga_se_odds[,1,2],ga_se_odds[,2,2], ga_se_odds[,1,3],ga_se_odds[,2,3] )
colnames(TabGa2) <-  c( "s.e.Ga(1-2)", "s.e.Ga(1-3)", "s.e.Ga(2-1)","s.e.Ga(2-3)","s.e.Ga(3-1)", "s.e.Ga(3-2)")
  
TabGa3 <- cbind(ga_z_score[,1,1],ga_z_score[,2,1],ga_z_score[,1,2],ga_z_score[,2,2],ga_z_score[,1,3],ga_z_score[,2,3])
colnames(TabGa3) <-  c("z-score(1-2)","z-score(1-3)","z-score(2-1)",  "z-score(2-3)","z-score(3-1)", "z-score(3-2)")

TabGa4 <- cbind(p[,1,1],p[,2,1],p[,1,2],  p[,2,2],p[,1,3],p[,2,3])
colnames(TabGa4) <-  c("p-value(1-2)", "p-value(1-3)", "p-value(2-1)","p-value(2-3)", "p-value(3-1)", "p-value(3-2)")

round(TabGa1, 3)
round(TabGa2, 3)
round(TabGa3, 3)
round(TabGa4, 3)

quant_all_cov_socio$bic


```

