---
title: "Q's Data Imputation"
output: html_document
date: '2022-11-25'
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("pacman")
pacman::p_load(tidyverse, dplyr)
```

```{r setup, include=FALSE}
#Qs <- read_csv("clean_Q.csv")
```

Okay so the struggle here is that we have a billion NA's this can be fixed by to methods (that both should be more sophisticated than just taking the mean):


**IMPUTATION**
HERE USING THE *MICE* PACKAGE 
```{r}
library(mice)
library(VIM)

### trying to visualise our NA's 
mice_plot <- aggr(Qs, col=c('navyblue','yellow'),
  numbers=TRUE, sortVars=TRUE,
  labels=names(Qs), cex.axis=.7,
  gap=3, ylab=c("Missing data","Pattern"))

```
this nicely illustrates how many we miss ... 

```{r}
imputed_Data <- mice(Qs, m=5, maxit = 50, method = 'pmm', seed = 500)
summary(imputed_Data)

```

``` {r}
#check imputed values
imputed_Data$imp$RimRemserUgen

```

```{r}
#get complete data ( 2nd out of 5)
completeData <- complete(imputed_Data,2)
```


## COMPARE DENSITY


### civilstatus
Cohabiting  == 1
Non-Cohabiting parents == 0
NA = NA

*Looks fine*
```{r}
# imputed data
hist(completeData$CivilStatus, main = "imputed data")

# non-imputed data
hist(Qs$CivilStatus, main = "NON-imputed data")

```


### uddannelse
Lang videregående uddannelse == 7
Mellemlang videregående uddannelse == 6
Kort videregående uddannelse ==5
Erhvervsuddannelsefaglært == 4
Ungdomsuddannelse fx HF == 3
10. Klasse == 2
7-9 Klasse == 1
NA = NA

*looks fine*
```{r}
# imputed data
hist(completeData$Uddannelse, main = "imputed data")

# non-imputed data
hist(Qs$Uddannelse, main = "NON-imputed data")
```

### I Uddannelse
. == 0
Ja == 1
Nej == 0
NA = NA

*looks finde
```{r}
# imputed data
hist(completeData$IUddannelse, main = "imputed data")

# non-imputed data
hist(Qs$IUddannelse, main = "NON-imputed data")
```


### Beskæftigelse 
I job = 1
Ikke i job = 0
Studerende = 0 
NA = NA

*looks fine*
```{r}
# imputed data
hist(completeData$Beskaeftigelse, main = "imputed data")

# non-imputed data
hist(Qs$Beskaeftigelse, main = "NON-imputed data")
```


### Arbejdstimer
Numeric values of working hours == numeric values
NA = NA

*looks fine*
```{r}
# imputed data
hist(completeData$Arbejdstimer, main = "imputed data")

# non-imputed data
hist(Qs$Arbejdstimer, main = "NON-imputed data")
```


### Indvandrestatus
NOTE: this variable is generated, not based on a reponse from parents
Dansk == 0
Udenlandsk == 1
NA = NA 

*looks fine*
```{r}
# imputed data
hist(completeData$Indvandrestatus, main = "imputed data")

# non-imputed data
hist(Qs$Indvandrestatus, main = "NON-imputed data")
```

### RimRemserUgen
0-1 gange = 1
2-3 gange = 2
4-5 gange = 3
mere end 5 gange = 4
NA = NA

*looks fine*
```{r}
# imputed data
hist(completeData$RimRemserUgen, breaks= 10, main = "imputed data")

# non-imputed data
hist(Qs$RimRemserUgen, main = "NON-imputed data")

```

### SangUgen 
0-1 gang = 1
2-3 gange = 2
4-5 gange = 3
mere end 5 gange = 4
NA = NA

*looks fine*
```{r}
# imputed data
hist(completeData$SangUgen, breaks= 10, main = "imputed data")

# non-imputed data
hist(Qs$SangUgen, main = "NON-imputed data")

```


### AntalBoerneboeger
Numeric values of AntalBoerneboeger == numeric values
NA = NA

*looks fine*
```{r}
# imputed data
hist(completeData$AntalBoerneboeger, breaks= 10, main = "imputed data")

# non-imputed data
hist(Qs$AntalBoerneboeger, main = "NON-imputed data")

```


### AntalVoksneboeger
0-20 == 1
20-50 == 2
50-100 == 3
100-200 == 4
Mere end 200 == 5
NA=NA

*looks fine* 
```{r}
# imputed data
hist(completeData$AntalVoksenboeger, breaks= 10, main = "imputed data")

# non-imputed data
hist(Qs$AntalVoksenboeger, main = "NON-imputed data")

```


### Modersmaal 
Dansk = 1
Andet modersmaal end dansk = 2
Tosproget = 3
NA=NA

*looks fine*
```{r}
# imputed data
hist(completeData$Modersmaal, breaks= 10, main = "imputed data")

# non-imputed data
hist(Qs$Modersmaal, main = "NON-imputed data")

```


### Pasningsform 
Dagpleje/vuggestue == 1
Integreret institution == 2
Hjemme == 3

*looks fine*
```{r}
# imputed data
hist(completeData$Pasningsform, breaks= 10, main = "imputed data")

# non-imputed data
hist(Qs$Pasningsform, main = "NON-imputed data")

```

### TimerIDagTilbud  
Faerre end 25 timer == 1
25-30 timer == 2
30-35 timer == 3
35-40 timer == 4
Mere end 40 timer == 5
NA == NA

*looks fine*
```{r}
# imputed data
hist(completeData$TimerIDagtilbud, breaks= 10, main = "imputed data")

# non-imputed data
hist(Qs$TimerIDagtilbud, main = "NON-imputed data")

```


### BekymningOmBarnetsSprog 
Ja == 1
Nej == 0

*looks fine*
```{r}
# imputed data
hist(completeData$BekymringOmBarnetsSprog, breaks= 10, main = "imputed data")

# non-imputed data
hist(Qs$BekymringOmBarnetsSprog, main = "NON-imputed data")

```


### BegyndtAtPludre
4-6 maaneder == 1
6-8 maaneder == 2
8-10 maaneder == 3
10-12 maaneder == 4
Endnu ikke == 5
Ved ikke == 6

*looks fine*
```{r}
# imputed data
hist(completeData$BegyndtAtPludre, breaks= 10, main = "imputed data")

# non-imputed data
hist(Qs$BegyndtAtPludre, main = "NON-imputed data")

```


### InitiativTilLaesning
Ja == 1
Nej == 0
NA =NA

*looks fine*
```{r}
# imputed data
hist(completeData$InitiativTilLaesning, breaks= 10, main = "imputed data")

# non-imputed data
hist(Qs$InitiativTilLaesning, main = "NON-imputed data")
```


### HoejtlaesningUgen 
0-1 gang = 1
2-3 gange = 2
4-5 gange = 3
mere end 5 gange = 4
NA=NA

*looks fine*
```{r}
# imputed data
hist(completeData$HoejtlaesningUgen, breaks= 10, main = "imputed data")

# non-imputed data
hist(Qs$HoejtlaesningUgen, main = "NON-imputed data")

```


### Write clean Q into csv 
```{r}
#write_csv(completeData, "/work/Bachelor/Q's/clean_Q_imputed.csv")
``` 


